\documentclass{scrartcl}
\usepackage[mathletters]{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{wasysym}
\usepackage{graphicx}
\usepackage[normalem]{ulem}
\usepackage{enumerate}

\usepackage{listings}

\lstset{ %
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
}


\title{MAIDEN QUEST}
\date{Thursday 20 November 2025}
\author{}

\begin{document}

\maketitle

		\section{MAIDEN QUEST}
Created Friday 24 October 2025



\section{one shot plot}
you are the Morgott's Guard of Gold. The elite of the elite of Leyndell. Soldiers among your ranks are chosen to join the Night's Cavalry. You're gathered and told of Mohg causing mischief in the sewers. 

In the sewers a gang of vulgar militia led by an omen or two stop you, blame the group for members of their gang going missing. in reality its Mohg and some revenants stealing away people from Leyndell and draining their blood in an attempt to amass enough red goo to bring back Mohg's love of his life: Miquella.



\subparagraph{If you run past enemies, you take some percent of the damage you took the first time you fought them.}


	Stone sword key that takes you to a fight with a revenant and then a grace before the final boss.
	


	One path leads to double lobster and esgar, then down a corridor to the old city and down to the boss. Before activating a lift down, there is a fanged imp door requiring a stonesword key to find a Revenant's hideout.
	
	

	Path leads to Volgar militia ambush and sewers
	
	Maybe they need a key for the old town section that is in this sewers or the opposite.
	


ambush room where there are ranged marrionettes shooting at them, and some small group they'll want to nuke

Maybe basilisks?

Imps or militia

Rats

Omens

Lobsters

Esgar +dogs

Revenant

Mini revenants with bells

Mohg





a boss is actually x kobolds ina trench coat

	every x boss turns is the same kobold
	
	so like swrod guy bow guy is the boss
	
	every other turn is a ranged attack
	






\section{Stats}
\begin{itemize}
\item All attributes range from 0 to 9.
\item You have 15 points to distribute. 
\item You can choose any equipment (mind your equip load!)
\item You can spend one attribute point to add a status effect to a weapon. 
\item You can spend one attribute point to acquire a consumable (cost doubles each purchase.)
\end{itemize}


\subparagraph{STR}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c| }
\hline
 Level & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\hline
 Melee Damage & 0 & 1 & 1 & 1 & 2 & 2 & 2 & 3 & 3 & 3 \tabularnewline
\hline
 HP & 12 & 12 & 14 & 14 & 16 & 16 & 18 & 20 & 22 & 24 \tabularnewline
\hline
\end{tabular}
\subparagraph{DEX}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c| }
\hline
 Level & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\hline
 Dexterity Mod & 0 & 1 & 1 & 1 & 2 & 2 & 2 & 3 & 3 & 3 \tabularnewline
\hline
 Extra Attacks & 0 & 0 & 0 & 1 & 1 & 1 & 2 & 2 & 2 & 3 \tabularnewline
\hline
 DR Bonus (¤) & 0 & 1 & 1 & 1 & 1 & 2 & 2 & 2 & 2 & 3 \tabularnewline
\hline
\end{tabular}
\subparagraph{END}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c| }
\hline
 Level & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\hline
 EQL ¤ \textless{}=L/M & 3/5 & 3/5 & 3/6 & 4/6 & 4/6 & 4/7 & 5/7 & 5/7 & 5/8 & 5/8 \tabularnewline
\hline
 Flask Dice & 2D4 & 2D4 & 2D4 & 2D4 & 2D4 & 2D6 & 2D6 & 2D6 & 2D6 & 2D6 \tabularnewline
\hline
 \#  Flasks & 1 & 2 & 2 & 2 & 3 & 3 & 3 & 4 & 4 & 4 \tabularnewline
\hline
 Status Bar & 1 & 1 & 1 & 2 & 2 & 2 & 3 & 3 & 3 & 4 \tabularnewline
\hline
\end{tabular}
\subparagraph{INT}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c| }
\hline
 Level & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\hline
 Mana Bonus & 0 & 0 & 1 & 1 & 2 & 2 & 3 & 3 & 4 & 4 \tabularnewline
\hline
 Spell Unlock Lvl & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\end{tabular}
\subparagraph{FTH}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c| }
\hline
 Level & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\hline
 Mana Bonus & 0 & 0 & 1 & 1 & 2 & 2 & 3 & 3 & 4 & 4 \tabularnewline
\hline
 Spell Unlock Lvl & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\end{tabular}
\subparagraph{MND}
\begin{tabular}{ |l|c|c|c|c|c|c|c|c|c|c| }
\hline
 Level & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \tabularnewline
\hline
\hline
 Bonus Flasks & +0 & +0 & +0 & +1 & +1 & +1 & +2 & +2 & +2 & +3 \tabularnewline
\hline
 Mana & 1 & 2 & 4 & 6 & 8 & 10 & 11 & 12 & 13 & 14 \tabularnewline
\hline
 Status Bar Bonus & +0 & +0 & +0 & +0 & +1 & +1 & +1 & +2 & +2 & +2 \tabularnewline
\hline
\end{tabular}


\section{Mana Pool (MP)}
You can spend MP to do the following:

\begin{itemize}
\item Cast a Spell (cost varies)
\item Buy an extra action (1 MP, cost increases by 1 after each use until resting at a Site of Grace)
\end{itemize}


\section{Flasks}
Your END determines how many flasks you have, with additional flasks granted from high levels of MND.

When you drink a flask you must first decide whether it is an HP or MP flask. Next you roll your flask dice and restore HP equal to the roll or MP equal to the higher of the two dice. 



\section{Status Effects}
When a character's Status Bar fills up, they suffer the effects of the last status gained. A character can only suffer from one status at a time.



\subparagraph{Blood Loss}
	\begin{itemize}
	\item The character immediately takes XD4 damage where X is the size of the character's status bar.
	\end{itemize}
\subparagraph{Chilled}
	\begin{itemize}
	\item Character adds -D6 to their DR. They lose chilled after rolling a 1.
	\end{itemize}
\subparagraph{Ablaze}
	\begin{itemize}
	\item Damage rolls vs target explode.
	\end{itemize}
\subparagraph{Poisoned}
	\begin{itemize}
	\item Character has half as many actions each round. A poisoned character rolls a D6 every turn, with poison ending when they roll a 1. 
	\end{itemize}
\subparagraph{Stunned}
	\begin{itemize}
	\item Character loses their next turn.
	\end{itemize}


\section{Armor}
\begin{itemize}
\item Depending on your Equip Load, you may also gain a DR bonus from high levels of DEX. 
\end{itemize}
\begin{tabular}{ |c|c|c| }
\hline
 Armor Type & DR & ¤ Weight \tabularnewline
\hline
\hline
 None & DR from DEX & ¤0 \tabularnewline
\hline
 Leather & D4 & ¤2 \tabularnewline
\hline
 Metal & D6+1 & ¤4 \tabularnewline
\hline
\end{tabular}


\section{Equip Load}
\emph{Each piece of equipment has an associated weight value (¤). Add the weights of your equipment and subtract your Strength Mod to get your equip load. Compare this to the Equip Load values granted by your Endurance Score.}

\begin{tabular}{ |c|c|c|c| }
\hline
   & Light Load & Medium Load & Heavy Load \tabularnewline
\hline
\hline
 Initiative & 2 & 4 & 6 \tabularnewline
\hline
\end{tabular}
At Light Load, you gain the full DR bonus from DEX (listed on the DEX table.)

At Medium Load, you gain half (rounded down) as much DR from DEX.



\subsection{Weapons}
\subparagraph{1H vs 2H}
\begin{itemize}
\item All weapons can be used with 1 hand (excluding bows) if you meet the One-Handed Requirement(s) (OHR)
\end{itemize}
\subparagraph{2H}
\begin{itemize}
\item You can wield any weapon with two hands, even if you do not meet the OHR.
\item If wielding a melee weapon with two hands your damage die goes up one step (D4 \textgreater{} D6 \textgreater{} D8 \textgreater{} D10 \textgreater{} D12)
\item When wielding any weapon with two hands, your off hand must be empty.
\end{itemize}


\section{Spellcasting Foci}


\paragraph{Staff ¤1}
	\begin{itemize}
	\item D2
	\item OHR: None
	\item Choose an INT requiring spell category, spells in that category gain +1 damage per die rolled.
	\end{itemize}


\paragraph{Seal ¤1}
	\begin{itemize}
	\item D2
	\item OHR: None
	\item Choose a FTH requiring spell category, spells in that category gain +1 damage per die rolled.
	\end{itemize}


\section{Fists}
\paragraph{Katar ¤1}
	\begin{itemize}
	\item D6
	\item OHR: None
	\item Unique Passive: If your attack is a 6, make another attack at -1.
	\end{itemize}
	

\paragraph{Iron Balls ¤1}
	\begin{itemize}
	\item D6
	\item OHR: STR 4
	\item Unique Passive: If powerstance attack dice match, target is Stunned.
	\end{itemize}


	

\section{Blades}
\paragraph{Katana ¤2}
	\begin{itemize}
	\item D6
	\item OHR: DEX 4
	\item Unique Passive: On your first attack versus a new target you roll one additional damage die.
	\end{itemize}
	

\paragraph{Twinblade ¤2}
	\begin{itemize}
	\item D6
	\item OHR: DEX 6
	\item Unique Passive: When outnumbered in melee you add 1 to your damage and DR. 
	\end{itemize}
	

\paragraph{Flamberge ¤4}
	\begin{itemize}
	\item D10
	\item OHR: STR 7
	\item Unique Passive: If damage roll is odd, ignore target's DR.
	\end{itemize}


\paragraph{Dagger ¤1}
	\begin{itemize}
	\item D4
	\item OHR: None
	\item Unique Passive: When an enemy misses an attack against you, you may make a dagger attack against them.
	\end{itemize}




\section{Polearms}
\paragraph{Spear ¤2}
	\begin{itemize}
	\item D6
	\item OHR: DEX 4
	\item Unique Passive: When an enemy moves to or through a space adjacent to you, you may make a free attack at them. max 1 attack per enemy.
	\end{itemize}
	

\paragraph{Scythe ¤3}
	\begin{itemize}
	\item D6
	\item OHR: STR 6
	\item Unique Passive: Also damages enemies adjacent to your target.
	\end{itemize}


\paragraph{Halberd ¤4}
	\begin{itemize}
	\item D8
	\item OHR: STR 8
	\item Unique Passive: Enemies up to 2 spaces away count as adjacent, and damage against them is rolled at advantage.
	\end{itemize}




\section{Blunt}
\paragraph{Flail ¤3}
	\begin{itemize}
	\item D6
	\item OHR: STR 5, DEX 5
	\item Unique Passive: Can attack twice at the cost of no attack next round.
	\end{itemize}


\paragraph{Giant Crusher ¤4}
	\begin{itemize}
	\item D10
	\item OHR: STR 10
	\item Unique Passive: If wielding this weapon with two hands roll 2D6 instead.
	\end{itemize}


\paragraph{Whip ¤1}
	\begin{itemize}
	\item D6
	\item OHR: DEX 6
	\item Unique Passive: Can attack targets up to 4 hexes away, optionally pulling them to you on a hit (or you to them if they are larger). 
	\end{itemize}


\section{Shields}
\paragraph{Buckler ¤2}
	\begin{itemize}
	\item D2
	\item OHR: STR 2
	\item Unique Passive: If an attack against you rolls its highest value, it misses, and you may immediately make a counter attack 
	\end{itemize}




\section{Ranged}
\emph{Bows cannot be used in melee range.}

\emph{Ammunition: Normal arrows and bolts are infinite, projectiles that apply statuses can be purchased.}

\paragraph{Shortbow (2H) ¤2}
							\begin{itemize}
							\item D6
							\item OHR: N/A
							\item Unique Passive: If your attack roll is odd you may continue attacking until you miss.
							\end{itemize}
						

\paragraph{Greatbow (2H) ¤4}
							\begin{itemize}
							\item D10
							\item OHR: N/A
							\item Unique Passive: Your arrows pierce targets up to your Strength score.
							\end{itemize}
						

\paragraph{Light Crossbow ¤2}
							\begin{itemize}
							\item D6
							\item OHR: DEX 6
							\item Unique Passive: Can be reloaded and fired an additional time if you used less than half your movement this turn.
							\end{itemize}
						

\paragraph{Hand Ballista (2H) ¤4}
							\begin{itemize}
							\item D10
							\item OHR: N/A
							\item Unique Passive: Cannot fire on the same turn as moving, but attack rolls are at advantage.
							\end{itemize}




			

\section{Consumables}


\subparagraph{• Kukri (2x)}
	\begin{itemize}
	\item 8 Range
	\item Attracts attention
	\item D4 weapon.
	\end{itemize}
\subparagraph{• Cracked Pot (1x)}
	\begin{itemize}
	\item 6 Range 
	\item Applies 2 stacks of a status of your choice (decided at time of purchase).
	\end{itemize}
\subparagraph{• Stonesword Key (1x)}
	\begin{itemize}
	\item Breaks an imp statue's seal.
	\end{itemize}
\subparagraph{• Status Ammunition (D6)}
	\begin{itemize}
	\item Ammunition that applies a status effect of your choice. 
	\item Roll the D6 after every attack, on a 1 you run out. 
	\end{itemize}




\section{Combat}
On your turn in combat you have two actions. Spend an action to do one of the following:

\subparagraph{• Move up to 6 hexes}
\subparagraph{• Make an attack}
	\begin{itemize}
	\item \emph{Attack with Mainhand or Offhand} 
	\item \emph{Powerstance Attack}
	\end{itemize}
\subparagraph{• Use a consumable}
\subparagraph{• Other action (unlock door, pull thing, etc)}
\begin{itemize}
\item \emph{Swapping equipment is a free action.}
\end{itemize}
	



\paragraph{Attacking}
\emph{To make an attack, roll your weapon's damage die.} 

\begin{itemize}
\item On a natural 1, you miss. 	
\item If the roll was even you apply one stack of your weapon's status effect (if applicable).
\item Total damage is equal to the roll + STR damage mod (if melee)
\end{itemize}
													

\paragraph{Powerstance Attack}
\emph{If you have the same weapon or weapon type equipped in your main and off hands, you may make a Powerstance Attack.} 

\begin{itemize}
\item Roll both weapon's damage dice and choose one as damage.
\item Apply one weapon's status build-up for each die that rolled an even number.
\end{itemize}


\subsection{Getting hit}
When you are hit by an attack you can either:

\subparagraph{Take the hit:}
	Reduced the incoming damage by:
	
	\begin{itemize}
	\item Rolling your armor's DR die, if you're wearing any.
	\item Any DR bonus granted from your Dexterity (if under Light Load, or half as much if under Medium Load).
	\item Any remaining damage after subtracting all sources of DR is removed from your HP.
	\end{itemize}
\subparagraph{Roll!}
	\begin{itemize}
	\item Burn an action this round and avoid all damage.
	\item You can only roll if you have an action to burn. If you've already acted in the current combat round and you used both of your actions, you're out of luck.
	\end{itemize}




\paragraph{Zero HP}
When you take damage that would reduce your health to zero or less, you are incapacitated. On your turn, an incapacitated character may crawl up to three hexes.

If your whole party is incapacitated, Game Over. (Respawn at last Site of Grace)



\begin{itemize}
\item When a character is incapacitated, their allies can revive them. To do so an ally needs to spend an action attacking you. They roll damage as usual. Treat the rolled damage as healing to the incapacitated character (do not subract the target's DR), If that brings their health above 0, they are back up and in the fight and can act as usual on their next turn.  
\item If you have already been incapacitated this combat, any incoming damage (healing) is halved.
\end{itemize}


\subsection{Initiative}
Every round of combat is split into six phases. Enemies act on 1, 3, and 5, while players act on phases 2, 4, and 6. What phase a character acts on is determined by their Equip Load.



At the start of each combat round, slow enemies telegraph one or more of their actions. In addition, when each player phase starts the Maiden Master will telegraph the actions of the enemies in the following phase. 



\paragraph{A Combat Round:}
\begin{enumerate}[1]
\item Slow enemies declare their intent.
\item Fast enemies act
	\begin{enumerate}[a]
	\item Average enemies declare their intent.
	\end{enumerate}
\item Light players act
\item Average enemies act
\item Medium players act
\item Slow enemies act
\item Heavy players act
\end{enumerate}


\paragraph{Bosses}
During boss fights, the boss (or their lair) will act on each enemy turn. At the end of each of it's turns, the boss \emph{may} telegraph its next action.







\section{Glintstone Sorcery}
\emph{Requires INT 1}

\subparagraph{Glintstone Pebble (1)}
\emph{Fire a small chunk of starlight.}

\begin{itemize}
\item D6 
\item Range: Near
\end{itemize}


\subparagraph{Rain of Stars (3)}
\emph{Release a downpour of raining stars.}

\begin{itemize}
\item 1D4
\item Range: Far
\item AOE: diameter 5 circle
\item Damage dealt the first time a character enters the area or starts its turn there.
\item AOE diameter shrinks by 1 on your next turn, centered on any point in the original AOE.
\end{itemize}


\subparagraph{Comet Azur (X)}
A \emph{continuous starry torrent cuts through the air.}

\begin{itemize}
\item XD4
\item Range: Near
\item AOE: 6 hex long, 1 hex wide line
\item Roll XD4, dealing damage to all characters in the AOE. For any dice that roll their maximum value, replace them with a die one step higher and repeat. (D4, D6, D8, D10, D12) 
\end{itemize}




\section{Gravity Sorcery}
\emph{Requires INT 1}

\subparagraph{Rock Sling (2)}
\emph{Tear rocks from the earth and send them flying.}

\begin{itemize}
\item 3D8
\item Range: Near
\item Roll 3D8, deal rolled damage to the target for each roll \textgreater{}= 4.
\item If all three rocks hit the target is Stunned.
\end{itemize}


\subparagraph{Blades of Stone (4)}
\emph{Blade-like clumps of rock erupt from the earth dealing damage then shattering after a short delay.}

\begin{itemize}
\item 2D4
\item Range: Near
\item AOE: 4 adjacent hexes
\item At the start of your next turn the rocks shatter and characters on or adjacent to the effected hexes take 2D4 damage and are Dazed.
\end{itemize}


\subparagraph{Meteorite (8)}
\emph{Tear the fabric of space and summon a shower of meteors to rain down onto the battlefield.} 

\begin{itemize}
\item 6D10
\item Range: Far
\item AOE: diameter 3 circle
\item Roll 6d10. Highest roll is damage of each meteor. For each die: Choose a target hex. On a 7+ the meteor hits the target. on a 1-6 the meteor misses in that direction (count hex faces clockwise) by 1d4 hexes. Damage is dealt to all characters on or adjacent to a struck hex. Any character that suffers two direct hits is Stunned.
\end{itemize}




\section{Pyromancy}
\emph{Requires FTH 1}

\emph{All pyromancy damage dice explode.}

\subparagraph{Catch Flame (2)}
\emph{A surging flame bursts from your hand.} 

\begin{itemize}
\item D6
\item Range: Close
\item AOE: 2 adjacent hexes, one must be Close.
\end{itemize}


\subparagraph{Flame, Fall Upon Them (5)}
\emph{You throw a handful of embers into the air that roar to life and rain down upon your enemies.}

\begin{itemize}
\item D6
\item Range: Near
\item AOE: Choose 5 hexes in a 5 diameter circle. 
\end{itemize}


\subparagraph{Fire's Deadly Sin (6)}
\emph{Summon six pillars of flame on nearby hexes and set self ablaze.}

\begin{itemize}
\item 2D4
\item Range: Near
\item Choose six hexes to summon flame upon. When a character first enters a pillar or start's its turn there they take damage.
\item Caster takes 1d4 damage each round the spell is active, and can end the spell at will.
\end{itemize}




\section{Miracles}
\emph{Requires FTH 1}

\subparagraph{Golden Vow (2 per ally)}
\emph{You greatly increase the power of your allies.} 	

\begin{itemize}
\item N/A
\item Range: Close
\item Selected allies gain +1 to attacks, flask regeneration, and DR for two turns.   
\end{itemize}


\subparagraph{Blessing's Boon (4)}
\emph{Grant the blessing of life to you and your allies.}

\begin{itemize}
\item D4
\item Range: Close
\item Choose up to (INT + FTH) characters to grant the blessing. Each blessed character heals D4 HP at the start of each of their turns. Blessing ends if the character is full health or ends their turn more than 3 hexes away from the caster.
\end{itemize}


\subparagraph{Elden Stars (7)}
\emph{A stream of golden shooting stars haunt your foes.}

\begin{itemize}
\item D4, 3D6
\item Range: Far
\item AOE: 3 diameter circle
\item Summon a golden shooting star on your hex. On your turn you may move the star two hexes and fire two bolts of golden light at up to two characters Near the shooting star. Bolts deal D4 damage. At any point you may detonate the star dealing 3D6 damage to all characters in a 3 diameter circle.   
\end{itemize}




\section{Golden Order Incantations}
\emph{Requires INT \$ FTH 1}

\subparagraph{Discus of Light (2)}
\emph{Throw out a ring of light that returns after a delay.}

\begin{itemize}
\item D6, D8
\item Range: Near
\item Choose a hex on the edge of your range (\textless{}=6 Hexes) or a terrain feature that is closer. Enemies along that line take D6 damage as the discus flies to your target. At the end of your next turn the discus returns to you dealing D8 damage to any characters along its path. Any enemies that share a space with your discus before it's return take D6 damage at the start of their turn. 
\end{itemize}


\subparagraph{Wrath of Gold (3)}
\emph{A wave of golden force crashes against nearby foes.}

\begin{itemize}
\item 2D6
\item Range: Close
\item Roll 2d6. All characters in Close range that you designate are pushed away from you a number of hexes equal to the roll of one die, and take damage equal to the roll of the other die.   
\end{itemize}


\subparagraph{Law of Causality (6)}
\emph{Retaliate against those who spurn the Grace of Gold.}

\begin{itemize}
\item D10
\item Range: Near
\item When an enemy attacks you or an ally you can see within range, you may choose to deal damage to the attacker and reduce the damage taken by D10. When you use this effect reduce the damage die one step. D10 \textgreater{} D8 \textgreater{} D6 \textgreater{} D4 Spell ends after rolling the D4.
\end{itemize}


















Quickstep (1): After attacking or being attacked you may move 1 hex in any direction.



Endure (x): Increase DR by x until your next turn.



Unsheath  (2): If this is your first attack against a target roll an additional damage die.



barrage: shoot until you miss



\end{document}
